---
title: 'Main Analysis'
author: "Felix Heim, Jana Schneider, Jana, Leon"
date: "December 5, 2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Claim 1 - Search Data Cases


## Claim 2 - Strict lockdown measures have prevented a thorough spread in South Korea

**Our initial motivation:**

* After a massive increase in daily cases, it appears that the government of South Korea was able to reduce the number of daily cases remarkably within a few days and continued to retain a constant low level.


**Claim description in more detail:**

* Stricter lockdown measures lead to a lower outbreak of the Covid-19 Virus 
* Compared to other countries, for example Germany, the government of South Korea reacted more effectively and efficiently 


**Our approach:**

* We first compared the daily cases of South Korea with the ones of Germany.
* Next we looked at the different types of government policy' measures.
* Within each type of policy we analysed the different measures in terms of time to daily cases.


```{r echo=FALSE}
#import libraries 

library(magrittr)
library(data.table)
library(ggplot2)
library(ggpubr)
```

```{r echo=FALSE}
# import files: Time, RKI data
time <- fread("./extData/Time.csv")
policy <- fread("./extData/Policy.csv")
RKI_data <- fread("./extData/DE_InfectionCases.csv")
patientinfo <- fread("./extData/PatientInfo.csv")
```


### Claim 2 - 1. Plot

```{r echo=FALSE, message=FALSE, include=FALSE}
#total cases in Korea per day
time[,confirmed_date:=as.Date(date,"%d/%m/%y")]
time[, confirmed_date:= as.IDate(confirmed_date)]

# total cases Germany
RKI_data <- RKI_data[, "Anzahl COVID-19-Fälle kumuliert" := NULL]

RKI_data_UsFormat <- RKI_data[, confirmed_date := as.Date(Berichtsdatum, 
                                                          format ="%d.%m.%y")]
#change date class to "IDate"
RKI_data_UsFormat[, confirmed_date:= as.IDate(confirmed_date)]
RKI_data_UsFormat <- RKI_data_UsFormat[, Berichtsdatum := NULL]



merge_GermanyUS <- merge(RKI_data_UsFormat, time, 
                         by = "confirmed_date", all.y = TRUE)


# plot
plot_germany <- ggplot(merge_GermanyUS, aes(x=confirmed_date)) + 
  geom_line(aes(y=`daily_cases`,color="Germany"))+
  geom_line(aes(y=`Anzahl Covid-Fälle pro Tag`,color="South Korea")) + 
  labs(x= "confirmed date", y="daily cases")+
  geom_rect(aes(xmin=as.Date('2020-02-26'),xmax=as.Date('2020-03-15'),
                ymin=860,ymax=890,color="18 days"))+
  geom_rect(aes(xmin=as.Date('2020-03-10'),xmax=as.Date('2020-05-10'),
                ymin=6400,ymax=6430,color="61 days"))+
  theme(legend.position="bottom") +
  theme(legend.title=element_blank()) 


```



```{r  echo=FALSE}
plot(plot_germany)
```

###### Short Analysis
* The total number of daily cases in South Korea compared to Germany is considerably lower. Considering the population of each country(~50 Mio. vs. 80 Mio.) this seems to be an outstanding achievement.
*Compared to Germany, it seems that South Korea needed less time to reduce and control the number of daily cases after the first outbreak of the virus. It took Germany about three times as long as South Korea to get the number of daily cases to a low level.  



### Claim 2 - 3. Plot

```{r echo=FALSE}

#total number of infection cases due to immigration
contact_overseas <- patientinfo[infection_case == "overseas inflow", 
                                 .N, by = "confirmed_date"]

#get subsets only for 3 different immigration policies 
#IP_Special, IP_14Day, IP_ManTest
immigration_policy <- policy[type == "Immigration"]

IP_Special <- immigration_policy[gov_policy == "Special Immigration Procedure"]
IP_14Day <- immigration_policy[gov_policy == "Mandatory 14-day Self-Quarantine"]
IP_ManTest <- immigration_policy[gov_policy == "Mandatory Self-Quarantine & Diagonostic Tests"]


#1. Run plot and safe it in overseas_plot
#2. Go to file "Lockdown_immigration" and run the code at the very end to get
#the figure


overseas_plot <- ggplot(contact_overseas, aes(x=confirmed_date, y=N)) + geom_line() +
  geom_vline(data = IP_Special, aes(xintercept = start_date, 
                                    color = "Immigration\nprocedure"), 
             linetype = "longdash", show.legend = TRUE)+
  geom_vline(data = IP_14Day, aes(xintercept = start_date, 
                                  color = "Self\nquarantine"), 
             linetype = "longdash", show.legend = TRUE)+
  geom_vline(data = IP_ManTest, aes(xintercept = start_date, 
                                    color = "Diagnostic\nTest US"), 
             linetype = "longdash", show.legend = TRUE) +
  labs(x = "confirmed date", y = "daily cases (overseas inflows)") +
  theme(legend.position="bottom") +
  theme(legend.title=element_blank()) 



```

```{r echo=FALSE}
#total cases in Korea per day
time[,confirmed_date:=as.Date(date,"%d/%m/%y")]



immigration_policy <- policy[type == "Immigration"]

IP_Special <- immigration_policy[gov_policy == "Special Immigration Procedure"]
IP_14Day <- immigration_policy[gov_policy == "Mandatory 14-day Self-Quarantine"]
IP_ManTest <- immigration_policy[gov_policy == "Mandatory Self-Quarantine & Diagonostic Tests"]

immigration_plot <- ggplot(time, aes(x=confirmed_date, y=daily_cases)) + geom_line() +
  
  geom_vline(data = IP_Special, aes(xintercept = start_date, 
                               color = "Immigration\nprocedure"), 
             linetype = "longdash", show.legend = TRUE)+
  geom_vline(data = IP_14Day, aes(xintercept = start_date, 
                                       color = "Self\nquarantine"), 
             linetype = "longdash", show.legend = TRUE)+
  geom_vline(data = IP_ManTest, aes(xintercept = start_date, 
                                 color = "Diagnostic\nTest US"), 
             linetype = "longdash", show.legend = TRUE)  +
  labs(x = "confirmed date", y = "daily cases") + 
  theme(legend.position="bottom") +
  theme(legend.title=element_blank()) 
```

```{r echo=FALSE}
#1. Run plot in file: Lockdown_overseas
#2. Run plot in Lockdown_immigration (current file)
#Execute code below to get both plots next to each other
plot_immigration <- ggarrange(immigration_plot, overseas_plot,
          ncol = 2, nrow = 1)
annotate_figure(plot_immigration,
                top = text_grob("International measures", 
                                color = "black", size = 14))

```

###### Short Analysis
* After the number of daily cases related to overseas inflow reached a very high level, the government of South Korea imposed a mandatory 14-day Self-Quarantine. It seems that after a short time the number of daily cases related to overseas inflow could be reduced sharply and retained a relatively stable level.
* After experiencing a peak in numbers, the government of South Korea establisehd special immigration procedures for foreign countries in order to prevent another severe increase in numbers caused by people entering the country. However, one can note that shortly afterwards the number of daily cases related to overseas inflow first increased before plunging afterwards. 
 

### Claim 2 - 4. Plot

```{r echo=FALSE}
#total cases in Korea per day
time[,confirmed_date:=as.Date(date,"%d/%m/%y")]
time[, confirmed_date:= as.IDate(confirmed_date)]


#extract education measures from table policy
date_education <- policy[type == "Education"]


#plot start of education policies +
#administration policies +
#social policies
#on infection cases per day within the time frame 

ggplot(time, aes(x=confirmed_date, y=daily_cases)) + geom_line() +
  
  #education policies
  
  geom_rect(aes(xmin=as.Date('2020-03-02'),xmax=as.Date('2020-04-06'),
                ymin=740,ymax=743,color="School delay"))+
  geom_text(aes(x = as.Date('2020-03-02'), y = 750, label = "School delay"),
    size = 3, vjust = 0, hjust = 0, color = "black")+
  
  geom_rect(aes(xmin=as.Date('2020-04-09'),xmax=as.Date('2020-06-08'),
                ymin=740,ymax=743,color="Online classes"))+  
  geom_text(aes(x = as.Date('2020-04-09'), y = 750, label = "Online classes"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  
  #social policies 
  
  geom_rect(aes(xmin=as.Date('2020-02-29'),xmax=as.Date('2020-04-19'),
                ymin=840,ymax=843,color="Strong social\ndistancing campaign"))+
  geom_text(aes(x = as.Date('2020-02-29'), 
                y = 850, label = "Strong Social distancing campaign"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  
  geom_rect(aes(xmin=as.Date('2020-04-19'),xmax=as.Date('2020-06-30'),
                ymin=840,ymax=843,color="Weak social\ndistancing campaign"))+
  geom_text(aes(x = as.Date('2020-05-01'), 
                y = 850, label = "Weak social distancing campaign"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  
  #administrative policies
  
  geom_rect(aes(xmin=as.Date('2020-05-08'),xmax=as.Date('2020-06-07'),
                ymin=110,ymax=113,color="Close bars\nand clubs"))+
  geom_text(aes(x = as.Date('2020-05-08'), 
                y = 120, label = "Close bars and clubs"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  geom_rect(aes(xmin=as.Date('2020-05-16'),xmax=as.Date('2020-06-30'),
                ymin=170,ymax=173,color="Local government\nadministrative orders"))+
  geom_text(aes(x = as.Date('2020-05-16'), 
                y = 180, label = "Local gov. administrative orders"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  geom_rect(aes(xmin=as.Date('2020-05-21'),xmax=as.Date('2020-06-03'),
                ymin=230,ymax=233,color="Close karaoke"))+
  geom_text(aes(x = as.Date('2020-05-21'), 
                y = 240, label = "Close karaoke"),
            size = 3, vjust = 0, hjust = 0, color = "black")+
  
  labs(x = "confirmed date", y = "daily cases",
       title="Administrative / Education / Social Measures")+
  theme(legend.position="none",plot.title= element_text(hjust=0.5)) 

```

###### Short Analysis
* After the number of daily cases have reached peak in March, numerous meausures with the aim of social distancing, such as delaying school start, were introduced. It seems that through these measures the number of daily cases could be reduced.
* In the begining of May, after the number of daily cases tended to increase again, further public indoor gathering places were forced closed. It seems that through that another severe outbreak was prevented.









---
**NOTE**

It works with almost all markdown flavours (the below blank line matters).

---


## Claim 3 - Region and Superspreaders



